The Hypothesis of Testing: Paradoxes arising out of reported coronavirus case-counts

### 2020-05-21 write-up/scifile.tex
Update scifile.tex

The goal of this paper is to express reservations at the use of case-counts as a proxy for disease prevalence and in estimation of standard epidemiological models for inference and forecasting.  The reason is straightforward: current models do not account simultaneously for selection bias and measurement error. In the US, for example, limited testing capacity has caused health departments to test only high-risk individuals.  Moreover, testing requires individuals to request a test and receive approval from their doctor.  Demands for increased testing capacity, while laudable, do not guarantee increased data quality.  Aggressive measures to increase testing capacity that decrease data quality may have a mitigated impact in our ability to estimate quantities of interest such as prevalence and effective reproduction number. We will demonstrate why there is a strong need for more precision and care in presenting COVID-19 analyses to the broader research and non-academic communities.

>>>>

The goal of this paper is to express reservations at the use of case-counts as a proxy for disease prevalence and in estimation of standard epidemiological models for inference and forecasting.  The reason is straightforward: current models do not account simultaneously for selection bias and measurement error. In the US, for example, individuals must to request a test and receive approval from their doctor. Demands for increased testing capacity, while laudable, do not guarantee increased data quality. We will demonstrate that there is limited information gain from increased testing when selection bias persists and testing inaccuracies potentially increase.
